In-silico molecular enrichment and clearance of the human intracranial space

### 2024-11-27 paper/main.tex

% respiratory pulsatility
Employing the same methodology, we estimate the respiratory contribution to dispersive mixing by computing the CSF flow field driven by an inflow of $0.121\,$ml/s \cite{liu2024using} and $1\,$ml/s across the lateral ventricular wall and the arachnoid mater, respectively. This amounts to a respiratory peak flow volume of $1.121\,$ ml/s at the craniocervical junction \cite{gutierrez2022effect}. While the resulting flow velocities are only about one fourth of their cardiac-induced counterparts (see \Cref{fig:csf}H and L), respiratory dispersive mixing reaches a factor of up to 350 due the lower respiratory frequency ($0.25\,$Hz) (\Cref{fig:csf}I and M).

>>>>

% respiratory pulsatility
Employing the same methodology, we estimate the respiratory contribution to dispersive mixing by computing the CSF flow field driven by an inflow of $0.121\,$ml/s \cite{liu2024using} and $1\,$ml/s \cite{gutierrez2022effect} across the lateral ventricular wall and the arachnoid mater, respectively. This amounts to a respiratory peak flow volume of $1.121\,$ ml/s at the craniocervical junction \cite{gutierrez2022effect}. While the resulting flow velocities are only about one fourth of their cardiac-induced counterparts (see \Cref{fig:csf}H and L), respiratory dispersive mixing reaches a factor of up to 350 due the lower respiratory frequency ($0.25\,$Hz) (\Cref{fig:csf}I and M).
